Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-11-26 paper/main.tex
nt commutative diagram

A functor preserves the structure of the category, namely morphisms and the source and target objects of those morphisms, composition of morphisms, and identity morphisms \cite{riehlCategoryTheoryContext}. Functors $\bm{F}: \mathcal{C}^{op} \rightarrow \mathcal{D}$ are called contravariant functors.

@@

The natural transformation composes with a functor such that the output is a compatible functor between the same categories 
\begin{equation}
  \label{eq:related-work:equivariance:natural-transform}
\begin{tikzcd}
  & {} \arrow[dd, "\alpha", Rightarrow, shorten=1.5em] &             \\
\mathcal{C} \arrow[rr, "F", bend left] \arrow[rr, "G"', bend right] &                                     & \mathcal{D} \\
  & {}                                  &            
\end{tikzcd}
\end{equation}
This means that $\alpha(F: \mathcal{C} \rightarrow \mathcal{D}) = G: \mathcal{C} \rightarrow \mathcal{D}$ commutes for any morphism $f:c\rightarrow c^{\prime}$ \cite{fongInvitationAppliedCategory2019}. A natural transform is a way to specify which functors between categories preserve the structure of the categories in the same manner. Arbitrary morphisms on sheaves are natural transforms \cite{SheafMathematics2021,bradleyWhatNaturalTransformation}.

>>>>

A functor preserves the structure of the category, namely morphisms and the source and target objects of those morphisms, composition of morphisms, and identity morphisms \cite{riehlCategoryTheoryContext}. For example, the functor $F:\mathcal{C} \rightarrow \mathcal{D}$ maps an object in $\mathcal{C}$ into an object in $\mathcal{D}$
\begin{equation}
\label{eq:related-work:equivariance:functor_diagram}
\begin{tikzcd}
  c \in Ob(\mathcal{C}) \arrow[d, "f"', shift right=8] \arrow[r, "F"] & F(c) \in Ob(\mathcal{D}) \arrow[d, "F(f)", shift right=8] \\
  c^{\prime} \in Ob(\mathcal{C}) \arrow[r, "F"']                       & F(c^{\prime}) \in Ob(\mathcal{D})                        
  \end{tikzcd}
\end{equation}
 such that for every morphism $f: c \rightarrow c^{\prime} \in Hom(\mathcal{C})$ there is a compatible morphism $F(f): F(c) \rightarrow F(c^{\prime}) \in Hom(\mathcal{D})$. Functors $\bm{F}: \mathcal{C}^{op} \rightarrow \mathcal{D}$ are called contravariant functors.

@@

\begin{equation}
  \label{eq:related-work:equivariance:natural-transform}
\begin{tikzcd}
  & {} \arrow[dd, "\alpha", Rightarrow, shorten=1.5em] &             \\
\mathcal{C} \arrow[rr, "F", bend left] \arrow[rr, "G"', bend right] &                                     & \mathcal{D} \\
  & {}                                  &            
\end{tikzcd}
\end{equation}
The natural transformation composes with a functor such that the output is a compatible functor between the same categories. This means that for every morphism $f: c \rightarrow c^{\prime}$ between objects in $\mathcal{C}$, there is a commutating naturality square for the corresponding objects in $\mathcal{D}$ \cite{milewskiCategoryTheoryProgrammers}. 
\begin{equation}
  \label{eq:related-work:equivariance:natural_transform_commute}
  \begin{tikzcd}
    c \arrow[rr, "F"] \arrow[rrrr, "G", bend left] \arrow[dd, "f"'] &  & F(c) \arrow[dd, "F(f)"'] \arrow[rr, "\alpha_{c}"] &  & G(c) \arrow[dd, "G(f)"] \\
                                                                    &  & {} \arrow[rr, "\alpha" description, dashed]       &  & {}                      \\
    c^{\prime} \arrow[rr, "F"] \arrow[rrrr, "G", bend right]        &  & F(c^{\prime}) \arrow[rr, "\alpha_{c^{\prime}}"]   &  & G(c^{\prime})          
    \end{tikzcd}
\end{equation}
\note{unpack this a drop more}
